Analysis for Non-Expressive performances (DURATION)

### 2020-04-08 material/analysis/stim_n/ioi_duration.Rmd
move seq plot
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

p_ioi_seq <- ggplot(data = ioi_seq, aes(x = RowNr, y = Mean, colour = SubNr)) +
  geom_line() +
  geom_point() +
  geom_hline(yintercept = 1, linetype = "dashed") + # Tempo
  geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width=.2,
                position = position_dodge(.05)) + 
  labs(x = "RowNr", y = "Normalised Duration") + scale_x_continuous(breaks=seq(1,66,1))
p_ioi_seq
```

# IOI
## 1. All - individual
- Average normDu for each participant.

@@

>>>>

# Duration
## 1. All - individual
- Average normDu for each participant.

@@

p_ioi_seq <- ggplot(data = ioi_seq, aes(x = RowNr, y = Mean, colour = SubNr)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width=.2,
                position = position_dodge(.05)) + 
  labs(x = "RowNr", y = "Normalised Duration") + scale_x_continuous(breaks=seq(1,66,1))
p_ioi_seq
```
